\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-04-14 main.tex
Update text

Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them. Films and holes are represented by instances of the \inline{superscreen.Polygon} class. All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film. \inline{Polygons} can constructed and combined using set-theoretic operations. Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$. Note that \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package~\cite{shapely}.

@@

While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values. For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value. This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function. For $N_h=1$, it is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}. For $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters. Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}. It is important to note that while \SuperScreen can calculate the field and current distributions or a given fluxoid state, the model does not capture transitions between fluxoid states.

@@

The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.  Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$ and  of $f(x, y)$ at the mesh vertices.

@@

We construct the two $p\times p$ gradient matrices $\nabla_x$ and $\nabla_y$, using the ``average gradient on a star" (or AGS) approach~\cite{Mancinelli2019-ci}. Briefly, we first construct two $t\times p$ matrices, $\vec{\nabla}_t=(\nabla_{t,x}, \nabla_{t,y})^T$ using ``per-cell linear estimation'' (or PCE)~\cite{Mancinelli2019-ci}, where $\nabla_{t,x}\mathbf{f}$ maps the field values at the vertices $\mathbf{f}$ to an estimate of the $x$-component of the gradient at the triangle centroids (centers-of-mass). The matrices $\nabla_x$ and $\nabla_y$ are then computed by, for each vertex $i$, taking the weighted average of $\nabla_{t,x}$ and $\nabla_{t,y}$ over adjacent triangles $t\in\mathcal{N}(i)$, with weights given by the angle between the two sides of the triangle adjacent to the vertex. The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively

@@

One can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Kogan2011-zn}:
\begin{align}
\begin{split}
    \label{eq:london_inhomogeneous_3d}
    \vec{H}(\vec{r})&=-\vec{\nabla}\times\left(\lambda^2(\vec{r})\vec{j}(\vec{r})\right)\\
    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + \vec{\nabla}\lambda^2(\vec{r})\times\vec{j}(\vec{r})\right).
\end{split}
\end{align}

In the 2D limit, i.e. a thin film with thickness $d\ll\lambda(x, y)$ lying parallel to the $x-y$ plane carrying sheet current density $\vec{J}(x, y)=\vec{j}(\vec{r})\cdot d$, we have:
\begin{align}
\begin{split}
    \label{eq:london_inhomogeneous_2d}
    \vec{H}(x, y)&=-\vec{\nabla}\times(\Lambda\vec{J})\\
    &=-\left(\Lambda\vec{\nabla}\times\vec{J}+\vec{\nabla}\Lambda\times\vec{J}\,\right)\\
    &=\left(\Lambda\nabla^2g+\vec{\nabla}\Lambda\cdot\vec{\nabla}g\right)\hat{z}
\end{split}
\end{align}
where $\Lambda=\Lambda(x, y)$, $g=g(x, y)$, $\vec{\nabla}=\left(\frac{\partial}{\partial x},\frac{\partial}{\partial y}\right)$, and $\vec{J}=\vec{J}(x, y)=\vec{\nabla}\times(g\hat{z})$.

If one defines an inhomogeneous effective penetration depth $\Lambda(x, y)$ in a \SuperScreen model, Equation~\ref{eq:london_inhomogeneous_2d} is solved numerically as follows. For a mesh with $p$ vertices, the penetration depth is represented by a $p\times 1$ vector $\mathbf{\Lambda}$. Equations~\ref{eq:Heff_sub_num} and \ref{eq:full_stream} are updated according to:
\begin{align}
\begin{split}
    \label{eq:Heff_inhomogeneous}
    &\mathbf{Q}.\mathbf{w}^T-\Lambda\mathbf{\nabla}^2\to\\
    &\mathbf{Q}.\mathbf{w}^T-\mathbf{\Lambda}^T.\mathbf{\nabla}^2-\vec{\nabla}\mathbf{\Lambda}\cdot\vec{\nabla}
\end{split}
\end{align}
The notation $\vec{\nabla}\mathbf{f}\cdot\vec{\nabla}$ indicates an inner (dot) product over the two spatial dimensions, resulting in a $p\times p$ matrix such that $(\vec{\nabla}\mathbf{f}\cdot\vec{\nabla})\mathbf{g}$ computes $(\vec{\nabla}f(x, y))\cdot(\vec{\nabla}g(x, y))$.

Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} with $\vec{\nabla}\Lambda\neq0$ do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for a simply-connected superconducting region $S$, where
\begin{equation}
	\Phi^f_S=\underbrace{\int_S\mu_0H_z(\pvec{r})\,\mathrm{d}^2r}_{\text{``flux part''}} + \underbrace{\oint_S\mu_0\Lambda(\pvec{r})\vec{J}(\pvec{r})\cdot\mathrm{d}\pvec{r}}_{\text{``supercurrent part''}}.
\end{equation}
As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies). The resulting current and field distributions, and the deviation from perfect fluxoid quantization, are shown in Figure~\ref{fig:inhomogeneous}.
%Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable. For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect. One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.

 \begin{code}
 \begin{minted}[fontsize=\small]{python}
 def linear_vs_angle(
     x: np.ndarray, y: np.ndarray, *, min_val: float, max_val: float
 ) -> np.ndarray:
     # Rotate the input coordinates so that theta = 0
     # corresponds to the slit position (along the -y axis).
     x, y = sc.geometry.rotate(
         np.stack(np.atleast_1d(x, y), axis=1), np.degrees(-np.pi / 2)
     ).T
     # Calculate the angular position of each mesh vertex.
     angles = np.arctan2(y, x) + np.pi  # range: [0, 2 * pi]
     # Set Lambda to increase linearly from min_val to max_val
     # as a function of angular position.
     Lambdas = angles / (2 * np.pi) * (max_val- min_val) + min_val
     return Lambdas

 # Define the Parameter and assign it as the Lambda of the superconducting layer.
 Lambda = sc.Parameter(linear_vs_angle, min_val=0.1, max_val=1.0)
 device.layers["base"].Lambda = Lambda
 # Everything below is identical to Code Block 1:
 # Calculate the device's response to a uniform applied field.
 applied_field = sc.sources.ConstantField(1)
 solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
 # Visualize the solution.
 # Plot the current density evaluated at each layer in the Device.
 solution.plot_currents()
 # Plot the magnetic field evaluated at each layer in the Device.
 solution.plot_fields()
 # Plot the field evaluated at any points in space.
 solution.plot_field_at_positions(device.points, zs=0.5)
 \end{minted}
 \captionof{listing}{Simulating an inhomogeneous superconducting device. Here we modify the superconducting ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the vector $\vec{r}=(x, y)$ and the $-y$ axis. See Figure~\ref{fig:inhomogeneous} for the resulting current and field distributions.}
 \label{code:inhomogeneous}
 \end{code}
 \begin{figure*}[h!]
     \centering
     \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $1\,\mathrm{mT}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$. ({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in pink. Dashed squares indicate regions $S$ for which we calculate the fluxoid $\Phi^f_S$ in panel ({\bf e}). ({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. ({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. ({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}). ({\bf e}) The fluxoid $\Phi^f_S$ for each of the six square fluxoid regions, $S$, shown with dotted lines in ({\bf a}). Unlike Equation~\ref{eq:london} (where $\Lambda$ is constant as a function of position), solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy fluxoid quantization, $\Phi^f_S=0$ for simply-connected superconducting regions $S$. $\Delta=\Phi^f_S / \int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is the deviation from perfect quantization, i.e. the total fluxoid expressed as a percentage of the flux part. In general we expect $\Delta$ to be largest in regions $S$ in which the gradient of the effective penetration depth $\vec{\nabla}\Lambda$ is large.}
     \label{fig:inhomogeneous}
 \end{figure*}

>>>>

Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them. Films and holes are represented by instances of the \inline{superscreen.Polygon} class. All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film. \inline{Polygons} can be constructed and combined using set-theoretic operations. Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$. Note that \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package~\cite{shapely}.

@@

While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values. For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value. This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function. For $N_h=1$, it is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}. For $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters. Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}. It is important to note that while \SuperScreen can calculate the field and current distributions for a given fluxoid state, the model does not capture transitions between fluxoid states.

@@

The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce the problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.  Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$  of $f(x, y)$ at the mesh vertices.

@@

We construct the two $p\times p$ gradient matrices $\nabla_x$ and $\nabla_y$, using the ``average gradient on a star" (or AGS) approach~\cite{Mancinelli2019-ci}. Briefly, we first construct two $t\times p$ matrices, $\vec{\nabla}_t=(\nabla_{t,x}, \nabla_{t,y})^T$ using ``per-cell linear estimation'' (or PCE)~\cite{Mancinelli2019-ci}, where $\nabla_{t,x}\mathbf{f}$ maps the field values at the vertices $\mathbf{f}$ to an estimate of the $x$-component of the gradient at the triangle centroids (centers-of-mass). The matrices $\nabla_x$ and $\nabla_y$ are then computed by, for each vertex $i$, taking the weighted average of $\nabla_{t,x}$ and $\nabla_{t,y}$ over adjacent triangles $t\in\mathcal{N}(i)$, with weights given by the angle between the two sides of the triangle adjacent to the vertex. The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively.

@@

The London equation (Equation~\ref{eq:london}) is valid only under the assumption that the London penetration depth $\lambda$, a proxy for the superfluid density, is constant as a function of position~\cite{Tinkham2004-zn}. In cases where the superfluid density varies as a function of position, Ginzburg-Landau theory provides a more accurate description of the magnetic response of the system. Nevertheless, in an effort to model inhomogeneous superconductors using London theory, one can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Cave1986-js, Kogan2011-zn}:
\begin{align}
\begin{split}
    \label{eq:london_inhomogeneous_3d}
    \vec{H}(\vec{r})&=-\vec{\nabla}\times\left(\lambda^2(\vec{r})\vec{j}(\vec{r})\right)\\
    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + \vec{\nabla}\lambda^2(\vec{r})\times\vec{j}(\vec{r})\right).
\end{split}
\end{align}

In the 2D limit, i.e. a thin film with thickness $d\ll\lambda(x, y)$ lying parallel to the $x-y$ plane carrying sheet current density $\vec{J}(x, y)=\vec{j}(\vec{r})\cdot d$, we have:
\begin{align}
\begin{split}
    \label{eq:london_inhomogeneous_2d}
    \vec{H}(x, y)&=-\vec{\nabla}\times(\Lambda\vec{J})\\
    &=-\left(\Lambda\vec{\nabla}\times\vec{J}+\vec{\nabla}\Lambda\times\vec{J}\,\right)\\
    &=\left(\Lambda\nabla^2g+\vec{\nabla}\Lambda\cdot\vec{\nabla}g\right)\hat{z},
\end{split}
\end{align}
where $\Lambda=\Lambda(x, y)$, $g=g(x, y)$, $\vec{\nabla}=\left(\frac{\partial}{\partial x},\frac{\partial}{\partial y}\right)$, and $\vec{J}=\vec{J}(x, y)=\vec{\nabla}\times(g\hat{z})$.

If one defines an inhomogeneous effective penetration depth $\Lambda(x, y)$ in a \SuperScreen model, Equation~\ref{eq:london_inhomogeneous_2d}, rather than Equation~\ref{eq:london}, is solved numerically as follows. For a mesh with $p$ vertices, the effective penetration depth is represented by a $p\times 1$ vector $\mathbf{\Lambda}$. Equations~\ref{eq:Heff_sub_num} and \ref{eq:full_stream} are updated according to:
\begin{align}
\begin{split}
    \label{eq:Heff_inhomogeneous}
    &\mathbf{Q}.\mathbf{w}^T-\Lambda\mathbf{\nabla}^2\to\\
    &\mathbf{Q}.\mathbf{w}^T-\mathbf{\Lambda}^T.\mathbf{\nabla}^2-\vec{\nabla}\mathbf{\Lambda}\cdot\vec{\nabla}
\end{split}
\end{align}
The notation $\vec{\nabla}\mathbf{f}\cdot\vec{\nabla}$ indicates an inner (dot) product over the two spatial dimensions, resulting in a $p\times p$ matrix such that $(\vec{\nabla}\mathbf{f}\cdot\vec{\nabla})\mathbf{g}$ computes $(\vec{\nabla}f(x, y))\cdot(\vec{\nabla}g(x, y))$ (see~\ref{appendix:laplace}).

Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for simply-connected superconducting regions $S$ in which $\vec{\nabla}\Lambda(\pvec{r})\neq0$ , where
\begin{equation}
	\Phi^f_S=\underbrace{\int_S\mu_0H_z(\pvec{r})\,\mathrm{d}^2r}_{\text{``flux part''}} + \underbrace{\oint_S\mu_0\Lambda(\pvec{r})\vec{J}(\pvec{r})\cdot\mathrm{d}\pvec{r}}_{\text{``supercurrent part''}}.
\end{equation}
%As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies). The resulting current and field distributions, and the deviation from perfect fluxoid quantization, are shown in Figure~\ref{fig:inhomogeneous}.
%Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable. For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect. One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.

% \begin{code}
% \begin{minted}[fontsize=\small]{python}
% def linear_vs_angle(
%     x: np.ndarray, y: np.ndarray, *, min_val: float, max_val: float
% ) -> np.ndarray:
%     # Rotate the input coordinates so that theta = 0
%     # corresponds to the slit position (along the -y axis).
%     x, y = sc.geometry.rotate(
%         np.stack(np.atleast_1d(x, y), axis=1), np.degrees(-np.pi / 2)
%     ).T
%     # Calculate the angular position of each mesh vertex.
%     angles = np.arctan2(y, x) + np.pi  # range: [0, 2 * pi]
%     # Set Lambda to increase linearly from min_val to max_val
%     # as a function of angular position.
%     Lambdas = angles / (2 * np.pi) * (max_val- min_val) + min_val
%     return Lambdas
%
% # Define the Parameter and assign it as the Lambda of the superconducting layer.
% Lambda = sc.Parameter(linear_vs_angle, min_val=0.1, max_val=1.0)
% device.layers["base"].Lambda = Lambda
% # Everything below is identical to Code Block 1:
% # Calculate the device's response to a uniform applied field.
% applied_field = sc.sources.ConstantField(1)
% solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
% # Visualize the solution.
% # Plot the current density evaluated at each layer in the Device.
% solution.plot_currents()
% # Plot the magnetic field evaluated at each layer in the Device.
% solution.plot_fields()
% # Plot the field evaluated at any points in space.
% solution.plot_field_at_positions(device.points, zs=0.5)
% \end{minted}
% \captionof{listing}{Simulating an inhomogeneous superconducting device. Here we modify the superconducting ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the vector $\vec{r}=(x, y)$ and the $-y$ axis. See Figure~\ref{fig:inhomogeneous} for the resulting current and field distributions.}
% \label{code:inhomogeneous}
% \end{code}
% \begin{figure*}[h!]
%     \centering
%     \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
%     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $1\,\mathrm{mT}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$. ({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in pink. Dashed squares indicate regions $S$ for which we calculate the fluxoid $\Phi^f_S$ in panel ({\bf e}). ({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. ({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. ({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}). ({\bf e}) The fluxoid $\Phi^f_S$ for each of the six square fluxoid regions, $S$, shown with dotted lines in ({\bf a}). Unlike Equation~\ref{eq:london} (where $\Lambda$ is constant as a function of position), solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy fluxoid quantization, $\Phi^f_S=0$ for simply-connected superconducting regions $S$. $\Delta=\Phi^f_S / \int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is the deviation from perfect quantization, i.e. the total fluxoid expressed as a percentage of the flux part. In general we expect $\Delta$ to be largest in regions $S$ in which the gradient of the effective penetration depth $\vec{\nabla}\Lambda$ is large.}
%     \label{fig:inhomogeneous}
% \end{figure*}
